The Local Group in the Cosmic Web

### 2014-10-21 paper/referee_reply.tex

\section{Minor Issues}

\begin{itemize}
\item
{\bf The general sample spans a greater range of masses than the x-axis. In Section 3 it is given as 5e11 to 5e13, whereas the x axis in fig 2 goes from 1e12 to 1e13, please explain.}

We have extended the mass range to 13.5 in the plots.

\item
{\bf In the discussion the authors say that "the MW satellites are located at high galactic latitude, almost perpendicular to the direction of M31." I take issue wth the "almost perpendicular" comment. The plane of MW satellites is between 32 and 45 degrees from the direction to M31 depending on how it is defined. This is a small point of contention in the literature because people define it differently given the uncertainties and incompleteness limits that drive the fact that most of these galaxies are found at high galactic latitude. 
Using a fairly conservative definition (ie the 11 brightest dwarfs for which we have fairly good completeness limits) Pawlowski et al 2012 and Shaya \& Tully 2014 both find something between 32 and 45 degrees. If the authors want to stick to the "almost perpendicular" statement they will need to justify it by citation and explanation}

@@

We have included the exact values in the Discussion section.

\item
{\bf I also want to note that the preferential accretion found by Libeskind et al 2014 shows a signal primarily along e3, but also defined as being away from e1. Indeed the accretion is somewhat planar in the e2-e3 plane. So I wouldn't say there is a contradiction.}

@@

We have made explicit this point in the Discussion section.

\item
{\bf Lastly the discussion and interpretation of results regarding the alignment of the orbital plane with the eigenvectors could do with an engagement of the vibrant debate in the literature regarding how massive haloes have a spin flip with respect the filament or wall they are in compared to less massive haloes (e.g. Aragon-Calvo et al 2007, Codis et al 2012, Trowland et al 2013, Libeskind et al 2013, among others), likely due to major mergers.}

### 2014-10-27 paper/main.tex
nueva version

\begin{abstract}
We explore the characteristics of the
cosmic web around Local Group(LG) like pairs  using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The sample of LG counterparts is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed for the LG.  
The second is a subset with additional observed kinematic constraints 
such as relative pair velocity and separation. 
We find that the pairs in the LG sample with all constraints are: (i)
Preferentially   located in filaments and sheets, (ii) Located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the pair orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane.
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignments with the cosmic web cannot be explained
by a simple mass dependency. 
Additionally, we fail to find a strong correlation of the spin of each
halo in the pair with the cosmic web.
Applied to the observed LG, there is a potential conflict between
these alignments and the evidence for satellite accretion along
filaments. 
This highlights the relevance of achieving a precise characterization
of the place of the LG in the cosmic web in the cosmological context
provided by $\Lambda$CDM.

@@

The spatial and kinematic configuration of the Local Group
(LG) galaxies is very uncommon in the local Universe and in cosmological
simulations. 
The LG is dominated by two big spirals: MW and M31, the next
most-luminous galaxy is M33 which is $\sim 10$ times less massive than
M31, followed by several dozen less luminous dwarf galaxies, up to a
distance of $\sim 3$\mpc.   
The velocity vector of M31, with a low
tangential velocity is consistent with a head-on collision orbit toward
the MW
\citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.

@@

@@

To better understand the properties of the LG and how this uncommon
pair configuration can be explained in the cosmological context, 
an immediate question arises: 
What else can we say of the environment of the LG on larger scales?

Observationally, the LG is located in a diffuse and
warped filament/wall connecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group \citep{2013AJ....146...69C}.
At this scale, there is no evident alignment of the MW-M31 orbital
plane with any local filament or the Virgo-Fornax direction. However,
if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
a clear alignment of the MW-M31 orbit with a local plane of galaxies
as shown by Figure $3$ in \citet{2013AJ....146...69C}.

We can then ask, to what extent is this an expected configuration in
$\Lambda$CDM? In particular, which are the typical/preferred locations
of these systems within the Cosmic Web?

%this paper.
In this \manuscript we study the large scale environment of LG 
analogues in the context of $\Lambda$CDM. 
We use the Bolshoi simulation to explore in what structures they
reside and if there is any correlation or alignment with the cosmic
web. 
The large scale environment is defined by the cosmic web components identified by
\citet{Tweb}, and we use the LG analogues computed by
\citet{lganalogues}.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.32\textwidth]{fig3a.pdf}
  \includegraphics[width=0.32\textwidth]{fig3b.pdf}
  \includegraphics[width=0.32\textwidth]{fig3c.pdf}
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
  the Tweb. 
The shaded region shows the expectation for a random
  distribution without any preferential alignment, it encloses the $5\%$ and $95\%$ percentiles of 5000
  flat distributions for $\mu$ generated with the  same number of
  points as the $2\sigma$ sample.  
    \label{fig:alignment_n}}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{fig5a.pdf}
  \includegraphics[width=0.45\textwidth]{fig5b.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal/radial vector $\hat{n}$/$\hat{r}$ (left/right)
  and each one of the  eigenvectors.  The lines show the trends for
  the general sample. The error bars in the 2$\sigma$ and 3$\sigma$ points
  correspond to jackknife estimates. 
  The shaded region shows the expectation for a random distribution
 without any preferential alignment, it encloses the $5\%$ and $95\%$
 percentiles of 5000  flat distributions for $\mu$ generated with the
 same number of points as the $2\sigma$ sample.   
\label{fig:median_alignment_n}}
\end{center}
\end{figure*}

@@

There are two important features in Figure \ref{fig:alignment_n}.
First the alignments themselves. 
There is a strong anti-alignment signature between $\hat{n}$ and the
third eigenvector. 
With respect to the second eigenvector the distribution is consistent
with no alignment. 
While for the first eigenvector there is a strong alignment, an expected
result considering the results with the other eigenvectors and
keeping in mind that they are orthonormal.
Second, the alignment strength changes for the different samples. 
For the anti-alignment with $\hat{e}_3$ the signal strengthens as we
move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.

@@

In the GS we already see an anti-alignment signature with the third eigenvector,
lower than for RS samples but still significant, this is an expected result,
even for random pairs with separations of the same order of the scale-length of 
underlying environment, just because individual pair members are more
likely to lie  following the density distribution. For instance, in a
filamentary density distribution, random  pairs are more likely to lie
along the filament; and in walls, random pairs are more likely to lie
in the wall.

Can the increase of the alignment strength in the different samples be
explained as a consequence of different mass dependencies as in the
results in the previous section? The answer is no. 
In Figure \ref{fig:median_alignment_n} we show the median of
$\mu\equiv\hat{e}_i\cdot\hat{n}$ and $\mu\equiv \hat{e}_i\cdot\hat{r}$
in different mass bins. 
Lines show the median $\mu$-mass relation for the three
eigenvectors in the GS, dots represent the results for the
2$\sigma$-3$\sigma$ samples.  Around the total mass $1.5-2.0 \times
10^{12}$ \msun in the RS samples, the median of $\mu$ clearly from the
2$\sigma$ and 3$\sigma$ samples clearly differs from the GS results.
Although in the GS the alignments have slight changes with mass, this
is not enough to explain the results for the reduced samples.

We also explored the main orbit differences between the GS and RS
which could be responsible of this alignment strength feature, and we
have that RS samples constraints the tangential velocity, then pair
orbits are more eccentric as we tighten pair constraints, and for GS sample there is no tangential velocity constraint at all.
Therefore, to study any relation between orbit eccentricity and alignment, we 
computed for each halo pair in all samples, an approximate orbit 
eccentricity assuming a two body orbit with masses set as the virial 
masses and initial conditions given by current velocity vector and separation.
We found that eccentricity is not responsible for this alignment feature by
selecting a subsample of GS having the same eccentricity than 
2$\sigma$-3$\sigma$ samples where we found no increase in the alignment when
compared with the full GS.

@@

We also find a stronger signal as we move into more restrictive
samples, although the signal from the GS is already very
significant. 
Quantitatively, the alignment feature with $\hat{e}_3$
means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
have $|\mu|>0.8$ ($<36$ degrees angle) and $\sim 25\%$ pairs have
$|\mu|>0.95$ ($<18$ degrees angle). Similar to the previous case of
the $\hat{n}$ vector, the increasing strength of the
$\hat{r}$ alignment cannot be explained by a selection on mass.

@@

The absence of alignment for the spins is consistent with different studies of
spin alingnemnt that mark the range $10^{12}$\Msun as either a transition mass
from alignment into anti-alignment or from no-alignment into alignment
\citep{Hahn2007,AragonCalvo2007,Zhang2009,Codis2012,Trowland2013,Libeskind2013,ForeroRomero2014}. We refer the reader to Table 2 in \cite{ForeroRomero2014}
for a review on the different results of spin alignment with the
cosmic web in cosmological simulations. It seems that this transition
has to do with the changes on the major merger rate as a dark matter
halo approaches the $10^{12}$\Msun mass \citep{2009MNRAS.399..762F,Codis2012}.

@@

However, the alignments with the cosmic web are 
mass-independent and seem to be stronger once the kinematic constraints
are imposed on the GS pairs. There is a clear anti-alignment between
the third eigenvector and the orbital angular momentum vector, meaning
that this vector is perpendicular to filaments and the sheets,  We
also found that the vector joining the LG halos are aligned with the
third eigenvector. This means that he pair is aligned with the filaments and
lies on the sheets and its motion is done along these directions.

@@

The most interesting feature is that these alignments are
tighter as we narrow the kinematic conditions of the LG towards the
observed values. A deeper understanding requires the study of the full
formation history and coevolution with the cosmic web, a task beyond
the scope of the work presented here.

How can we relate these alignments to the observed LG? 
To evaluate this point we use observational information for the
satellite distribution around the LG galaxies.  The MW satellites are
located at high galactic latitudes forming a planar structure that
forms an angle of $42^{\circ}-52^{\circ}$, $\mu=0.6-0.7$ with the
vector joining the MW and M31; while the M31 satellites are on a plane
that lies on the same vector \citep{Pawlowski2013,Shaya2013}.

Most $\Lambda$CDM studies find that sub-structure infall direction is
done along $\hat{e}_{3}$ (the direction of filaments)
\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B} or almost over the plane
defined by the $\hat{e}_2$ and $\hat{e}_3$ \cite{2014MNRAS.443.1274L}.

Taking this three points together (the alignment of MW-M31 along
$\hat{e}_3$, the observed satellite alignments and the preferential
infall along $\hat{e}_3$) we have that the M31 plane of satellites is
completely consistent with the average alignment picture we have
described. However, the plane defined by the MW satellites should
also be close to parallel with respect to the vector joining MW and
M31 and the plane of M31 satellites. Instead, this plane has
$\mu=0.6-0.7$ with respect to these directions. The spatial location
of MW satellites raise a potential contradiction with the average expectations
from $\Lambda$CDM, a point that has been raised before
\citep{Pawlowski2012,Pawlowski2014}.

@@

Our results raise the need to observationally constrain the
alignments of LG pairs with their cosmic web environment. To this end
one could use mass reconstructions from large surveys
\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S} to
select a LG sample to quantify the alignments with the surrounding
filamentary structure. This would allow not only a direct
quantification of how common are the LG alignments but also provide a
new test of $\Lambda$CDM.  We thank the referee Noam Libeskind for
suggestions that helped us to clarify and strenghten the results
presented in the paper.

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster. 
The authors would like to thank Andrey Kravtsov and Nelson Padilla
for their useful comments; and Yehuda Hoffman for insightful
conversations on the subject of the Local Group and the Cosmic Web. 
\bibliographystyle{apj}
\bibliography{references}

@@

Codis->spin
http://adsabs.harvard.edu/abs/2012MNRAS.427.3320C

I've just read the pre-print you had on the arXiv today (The Local Group in the Cosmic Web). You make some interesting comments about the distribution of the LG galaxies and their satellites, i.e. about a joint consideration of the MW-M31 orientation and their satellite systems. You might find it interesting that I have been working on this issue a lot lately (see in particular Pawlowski, Kroupa & Jerjen, 2013, MNRAS, 435, 1928 and Pawlowski & McGaugh, 2014, MNRAS, 440, 908). In addition to the satellite planes (VPOS around the MW, GPoA around M31), the more-distant dwarf galaxies in the LG are part of coherent and surprisingly symmetric structures, too.

Concerning the idea that the distribution of satellite galaxies is shaped by the accretion of sub-halos along filaments, I'd like to point out that this effect is not strong enough to explain the observed, very narrow and coherent satellite structures (e.g. the recent Pawlowski et al. 2014, MNRAS, 442, 2362, or Pawlowski et al., 2012, MNRAS, 424, 80). Thus, the accretion of sub-halos along filaments, as seen in dark matter simulations, is inconsistent with the observed satellite structures. A different explanation is required for the existence of the (co-orbiting) satellite planes. This might be a reason for the apparent conflict of your results and the filamentary

>>>>

\begin{abstract}
We explore the characteristics of the
cosmic web around Local Group(LG) like pairs  using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The sample of LG counterparts is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed for the LG.  
The second is a subset with additional observed kinematic constraints 
such as relative pair velocity and separation. 
We find that the pairs in the LG sample with all constraints are: (i)
Preferentially   located in filaments and sheets, (ii) Located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web.
The alignments are such that he pair orbital angular momentum tends to
be perpendicular to the smallest tidal eigenvector, $\hat{e}_3$, which
lies along the filament direction or the sheet plane.
A stronger alignment is present for the vector linking the two halos with the vector $\hat{e}_3$. Additionally, we fail to find a strong correlation of the spin of each halo in the pair with the cosmic web.
All these trends are expected to a great extent from the selection on
the LG total mass on the general sample. 
Applied to the observed LG, there is a potential conflict between
the alignments of the different planes of satellites and the numerical
evidence for satellite accretion along filaments; the direction
defined by $\hat{e}_3$. This highlights the relevance of achieving a
precise characterization of the place of the LG in the cosmic web in
the cosmological context provided by $\Lambda$CDM.

@@

The spatial and kinematic configuration of the Local Group
(LG) galaxies is very uncommon in the local Universe and in cosmological
simulations. 
The LG is dominated by two big spirals: the Milky Way (MW) and M31, the next
most-luminous galaxy is M33 which is $\sim 10$ times less massive than
M31, followed by several dozen less luminous dwarf galaxies, up to a
distance of $\sim 3$\mpc.   
The velocity vector of M31, with a low
tangential velocity is consistent with a head-on collision orbit toward
the MW
\citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.

@@

In addition, the LG is located in a diffuse and
warped filament/wall connecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group \citep{2013AJ....146...69C}.
At this scale, there is no evident alignment of the MW-M31 orbital
plane with any local filament or the Virgo-Fornax direction. However,
if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
a clear alignment of the MW-M31 orbit with a local plane of galaxies
as shown by Figure $3$ in \citet{2013AJ....146...69C}. On top of that,
the satellite galaxies in the MW and M31 present different kinds of
strong alignments along planes \citep{Pawlowski2013,Shaya2013}, which
are sometimes considered as unusual in the context of the $\Lambda$
Cold Dark Matter (CDM) model \citep{Pawlowski2012}.

@@

To better understand the properties of the LG and how this uncommon
pair configuration can be explained in the cosmological context, 
some questions arise. What else can we say of the environment of the
LG on larger scales? To what extent is this an expected configuration
in $\Lambda$CDM? In particular, which are the typical/preferred locations
of these systems within the Cosmic Web? Are the preferential
alignments of satellites a result of the location of the LG in the
Cosmic Web?

%this paper.
In this \manuscript we address those questions by studying the large
scale environment of LG  analogues in the context of \lcdm. 
We use the Bolshoi simulation to explore in what structures they
reside and if there is any correlation or alignment with the cosmic
web.  The large scale environment is defined by the cosmic web
components identified by \citet{Tweb}, and we use the LG analogues computed by
\citet{lganalogues}.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.32\textwidth]{fig3a.pdf}
  \includegraphics[width=0.32\textwidth]{fig3b.pdf}
  \includegraphics[width=0.32\textwidth]{fig3c.pdf}
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
  the Tweb. 
The shaded region shows the expectation for a random
  distribution without any preferential alignment, it encloses the $5\%$ and $95\%$ percentiles of 10000
  flat distributions for $\mu$ generated with the  same number of
  points as the $2\sigma$ sample.  
    \label{fig:alignment_n}}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{fig5a.pdf}
  \includegraphics[width=0.45\textwidth]{fig5b.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal/radial vector $\hat{n}$/$\hat{r}$ (left/right)
  and each one of the  eigenvectors.  The lines show the trends for
  the general sample. The error bars in the 2$\sigma$ and 3$\sigma$ points
  correspond to jackknife estimates. 
  The shaded region shows the expectation for a random distribution
 without any preferential alignment, it encloses the $5\%$ and $95\%$
 percentiles of 10000  flat distributions for $\mu$ generated with the
 same number of points as the $2\sigma$ sample.   
\label{fig:median_alignment_n}}
\end{center}
\end{figure*}

@@

There are two important features in Figure \ref{fig:alignment_n}.
First the alignments themselves. 
There is a strong anti-alignment signature between $\hat{n}$ and the
third eigenvector. 
With respect to the first and second eigenvector the distribution is consistent
with no alignment. 
Second, the alignment strength changes for the different samples. 
For the anti-alignment with $\hat{e}_3$ the signal strengthens as we
move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.

@@

The alignment strength could be explained to a great extend by 
a total mass dependency. In Figure \ref{fig:median_alignment_n} we
show the median of $\mu\equiv\hat{e}_i\cdot\hat{n}$ and $\mu\equiv
\hat{e}_i\cdot\hat{r}$ in different mass bins. 
Lines show the median $\mu$-mass relation for the three
eigenvectors in the GS, dots represent the results for the
2$\sigma$-3$\sigma$ samples.  Around the total mass $1.5-2.0 \times
10^{12}$ \msun in the RS samples, the median of $\mu$ clearly from the
2$\sigma$ and 3$\sigma$ samples clearly differs from the GS
results. However, the uncertainty level on the median for a small
sample (indicated by the shaded region) makes this trend compatible
with the values from the GS sample.

We also explored characteristics in the orbits which could be
responsible of the strengthen alignment feature. We  
have that RS samples constrains the tangential velocity, as a
consequence pair orbits are more eccentric as we tighten pair
constraints. For the GS sample there is no tangential velocity
constraint at all.
We studied the relationship between orbit eccentricity and alignment
computing for each halo pair in all samples an approximate orbit 
eccentricity assuming a two body orbit with masses set as the virial 
masses and initial conditions given by current velocity vector and separation.
We found that  selecting a subsample of GS having the same eccentricity than 
2$\sigma$-3$\sigma$ samples does not increase in the alignment when
compared with the full GS.

@@

We also find a stronger signal as we move into more restrictive
samples, although the signal from the GS is already very
significant. 
Quantitatively, the alignment feature with $\hat{e}_3$
means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
have $|\mu|>0.8$ ($<36$ degrees angle) and $\sim 25\%$ pairs have
$|\mu|>0.95$ ($<18$ degrees angle). Similar to the previous case of
the $\hat{n}$ vector, the increasing strength of the
$\hat{r}$ alignment can be explained to a great extenct by a selection
on mass.

@@

The absence of alignment for the spins is consistent with different studies of
spin alingnment that mark the range $10^{12}$\Msun as either a transition mass
from alignment into anti-alignment or from no-alignment into alignment
\citep{Hahn2007,AragonCalvo2007,Zhang2009,Codis2012,Trowland2013,Libeskind2013,ForeroRomero2014}. We refer the reader to Table 2 in \cite{ForeroRomero2014}
for a review on the different results of spin alignment with the
cosmic web in cosmological simulations. It seems that this transition
has to do with the changes on the major merger rate as a dark matter
halo approaches the $10^{12}$\Msun mass \citep{2009MNRAS.399..762F,Codis2012}.

@@

The alignments with the cosmic web have also a mass
dependency. Although they seem to be stronger once the kinematic constraints
are imposed on the GS pairs, the results are consistent with the
a simple mass cut on the GS sample. There is a clear anti-alignment between
the third eigenvector and the orbital angular momentum vector, meaning
that this vector is perpendicular to filaments and the sheets,  We
also found that the vector joining the LG halos are aligned with the
third eigenvector. This means that he pair is aligned with the filaments and
lies on the sheets and its motion is done along these directions.

@@

How can we relate these alignments to the observed LG? 
To evaluate this point we use observational information for the
satellite distribution around the LG galaxies.  The MW satellites are
located at high galactic latitudes forming a planar structure that
forms an angle of $42^{\circ}-52^{\circ}$ ($\mu=0.6-0.7$) with the
vector joining the MW and M31; while the M31 satellites are on a plane
that lies on the same vector \citep{Pawlowski2013,Shaya2013}.

Most $\Lambda$CDM studies find that sub-structure infall direction is
done along $\hat{e}_{3}$ (the direction of filaments)
\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B} or almost over the plane
defined by the $\hat{e}_2$ and $\hat{e}_3$ \citep{2014MNRAS.443.1274L}.

Taking this three points together (the alignment of MW-M31 along
$\hat{e}_3$, the observed satellite alignments and the preferential
infall along $\hat{e}_3$) we have that the M31 plane of satellites is
completely consistent with the average alignment picture we have
described. However, the plane defined by the MW satellites should
also be close to parallel with respect to the vector joining MW and
M31 and the plane of M31 satellites. Instead, this plane has
$\mu=0.6-0.7$ with respect to these directions. Therefore, we suggest
that the spatial location of MW satellites raises a potential
contradiction with the average expectations from $\Lambda$CDM, a point
that has been mentioned before \citep{Pawlowski2012,Pawlowski2014}.

@@

Our results raise the need to observationally constrain the
alignments of LG pairs with their cosmic web environment. To this end
one could use mass reconstructions from large surveys
\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014MNRAS.445..988N,
  2014ApJ...794...94W} or filament finders
\citep{2010MNRAS.407.1449G,2011MNRAS.414..350S} to select a LG sample
to quantify the alignments with the surrounding filamentary
structure. This would allow not only a direct quantification of how
common are the LG alignments but also provide a new test of
$\Lambda$CDM.

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster. 
The authors would like to thank Andrey Kravtsov and Nelson Padilla
for their useful comments; Yehuda Hoffman for insightful
conversations on the subject of the Local Group and the Cosmic Web;
and the referee Noam Libeskind  that helped us to clarify and
strenghten the results presented in the paper. 
\bibliographystyle{apj}
\bibliography{references}

@@
